Manuscript

### 2025-04-11 analysis/secondary_analyses.qmd
add table5

```{r}
library(foreign)
library(tidyverse)
library(semTools)
library(lavaan)
library(MBESS)
```

@@

```{r}
# Funktion zum Extrahieren standardisierter Ladungen (nur einmal definieren)
get_std_loadings <- function(fit, model_name) {
  standardizedSolution(fit) %>%
    filter(op == "=~") %>%
    select(lhs, rhs, est.std) %>%
    mutate(model = model_name)
}

# ---- Alter ----
loadings1 <- get_std_loadings(fit1A6, "age 1")
loadings2 <- get_std_loadings(fit1A2, "age d1")
all_loadings1 <- bind_rows(loadings1, loadings2)

table_loadings1 <- all_loadings1 %>%
  pivot_wider(names_from = model, values_from = est.std)

print(table_loadings1)

# ---- Größe ----
loadings3 <- get_std_loadings(fit1G6, "height 2")
loadings4 <- get_std_loadings(fit1G2, "height d2")
all_loadings2 <- bind_rows(loadings3, loadings4)

table_loadings2 <- all_loadings2 %>%
  pivot_wider(names_from = model, values_from = est.std)

print(table_loadings2)

# ---- Gewicht ----
loadings5 <- get_std_loadings(fit1Ge6, "weight 3")
loadings6 <- get_std_loadings(fit1Ge2, "weight d3")
all_loadings3 <- bind_rows(loadings5, loadings6)

table_loadings3 <- all_loadings3 %>%
  pivot_wider(names_from = model, values_from = est.std)

print(table_loadings3)

mod_indA6 <- lavaan::modificationindices(fit1A6)
subset(mod_indA6[order(mod_indA6$mi, decreasing=TRUE), ], mi > 4)
mod_indA2 <- lavaan::modificationindices(fit1A2)
subset(mod_indA2[order(mod_indA2$mi, decreasing=TRUE), ], mi > 4)
mod_indG6 <- lavaan::modificationindices(fit1G6)
subset(mod_indG6[order(mod_indG6$mi, decreasing=TRUE), ], mi > 4)
mod_indG2 <- lavaan::modificationindices(fit1G2)
subset(mod_indG2[order(mod_indG2$mi, decreasing=TRUE), ], mi > 4)
mod_indGe6 <- lavaan::modificationindices(fit1Ge6)
subset(mod_indGe6[order(mod_indGe6$mi, decreasing=TRUE), ], mi > 4)
mod_indGe2 <- lavaan::modificationindices(fit1Ge2)
subset(mod_indGe2[order(mod_indGe2$mi, decreasing=TRUE), ], mi > 4)
```

>>>>

```{r}
library(foreign)
library(tidyverse)
library(semTools)
library(lavaan)
```

@@

```{r}
load_df <- 
  bind_rows(
    standardizedSolution(fit1A6, type = "std.all") |> mutate(measure = "age", categories = "6"),
    standardizedSolution(fit1A2, type = "std.all") |> mutate(measure = "age", categories = "2"),
    standardizedSolution(fit1G6, type = "std.all") |> mutate(measure = "height", categories = "6"),
    standardizedSolution(fit1G2, type = "std.all") |> mutate(measure = "height", categories = "2"),
    standardizedSolution(fit1Ge6, type = "std.all") |> mutate(measure = "weight", categories = "6"),
    standardizedSolution(fit1Ge2, type = "std.all") |> mutate(measure = "weight", categories = "2")) |>
  filter(lhs == "f1" & op == "=~") |> 
  mutate(item_name = rhs) |>
  # Create new columns: prefix (everything before underscore) and suffix (the numeric part)
  mutate(prefix = sub("_.*", "", item_name),
    suffix = as.numeric(sub(".*_", "", item_name))) |>
  group_by(prefix) |>
  mutate(item = match(suffix, sort(unique(suffix)))) |>
  mutate(item = replace_na(as.character(item), "Physical item")) |>
  ungroup() |>
  mutate(est_print = papaja::printnum(est.std, gt1 = FALSE, digits = 3)) |>
  select(item, measure, categories, est_print) |>
  pivot_wider(names_from = c(measure, categories), values_from = est_print)

fit_df <- bind_rows(
  data.frame(as.list(fitMeasures(fit1A6))) |> mutate(measure = "age", categories = "6"),
  data.frame(as.list(fitMeasures(fit1A2))) |> mutate(measure = "age", categories = "2"),
  data.frame(as.list(fitMeasures(fit1G6))) |> mutate(measure = "height", categories = "6"),
  data.frame(as.list(fitMeasures(fit1G2))) |> mutate(measure = "height", categories = "2"),
  data.frame(as.list(fitMeasures(fit1Ge6))) |> mutate(measure = "weight", categories = "6"),
  data.frame(as.list(fitMeasures(fit1Ge2))) |> mutate(measure = "weight", categories = "2")
) |>
  pivot_longer(!c(measure, categories), names_to = "statistic", values_to = "est") |>
  filter(statistic %in% c("chisq.scaled", "pvalue.scaled", "df.scaled", "cfi.scaled", "rmsea.scaled", "srmr")) |>
  mutate(est_print = papaja::printnum(est, gt1 = FALSE, digits = 3)) |>
  pivot_wider(id_cols = statistic, names_from = c(measure, categories), values_from = est_print)

table5 <- rbind(
    load_df |> rename(Measure = item) |> mutate(group = "Items"),
    fit_df |> rename(Measure = statistic) |> mutate(group = "Fit")
  ) |> 
  group_by(group) |>
  flextable::as_grouped_data(groups = "group") |>
  flextable::as_flextable(hide_grouplabel = TRUE) |>
  flextable::add_header_row(values = c("Measure", "Age", "Height", "Weight"),
    colwidths = c(1, 2, 2, 2)) |>
  flextable::set_header_labels(
    values = list(
      Measure = "Categories",
      age_6 = "6", age_2 = "2", 
      height_6 = "6", height_2 = "2",
      weight_6 = "6", weight_2 = "2")) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table5
```

## Modification indices

```{r}
mod_indA6 <- lavaan::modificationindices(fit1A6)
subset(mod_indA6[order(mod_indA6$mi, decreasing=TRUE), ], mi > 4)
mod_indA2 <- lavaan::modificationindices(fit1A2)
subset(mod_indA2[order(mod_indA2$mi, decreasing=TRUE), ], mi > 4)
mod_indG6 <- lavaan::modificationindices(fit1G6)
subset(mod_indG6[order(mod_indG6$mi, decreasing=TRUE), ], mi > 4)
mod_indG2 <- lavaan::modificationindices(fit1G2)
subset(mod_indG2[order(mod_indG2$mi, decreasing=TRUE), ], mi > 4)
mod_indGe6 <- lavaan::modificationindices(fit1Ge6)
subset(mod_indGe6[order(mod_indGe6$mi, decreasing=TRUE), ], mi > 4)
mod_indGe2 <- lavaan::modificationindices(fit1Ge2)
subset(mod_indGe2[order(mod_indGe2$mi, decreasing=TRUE), ], mi > 4)
```

# Save Results for Manuscript

```{r}
results <- saveRDS(
  object = list(
    table5 = table5
    ), 
  file = "../results/results_secondary.rds"
)
```

### 2025-04-11 manuscript.qmd
add table5

results <- readRDS("results/results.rds")
```

@@

```{r}
#| label: "tbl-3"
#| tbl-cap: Standardized item loadings on the general latent variable for 6 categories controlling for the self-reported physical item and self-reported sex.
#| ft.align: left
#| disable-apaquarto-processing: false
#| apa-note: Loadings on the latent variable or standardized regression weights of the self-reported physical item and self-reported sex greater than .60 are printed in bold typeface.
results$table3
```

@@

```{r}
#| label: "table5"
```

>>>>

results <- readRDS("results/results.rds")
results_secondary <- readRDS("results/results_secondary.rds")
```

@@

```{r}
#| label: "tbl-3"
#| tbl-cap: Standardized item loadings on the general latent variable for 6 categories controlling for the self-reported physical item and self-reported sex.
#| ft.align: left
#| disable-apaquarto-processing: false
#| apa-note: Loadings on the latent variable or standardized regression weights of the self-reported physical item and self-reported sex greater than .60 are printed in bold typeface.

results$table3
```

@@

```{r}
#| label: "tbl-5"
#| tbl-cap: Latent variable loadings for 6 and 2 response categories with correlated errors 
#| ft.align: left
#| disable-apaquarto-processing: false
#| apa-note: CFI = Comparative Fit Index (scaled). RMSEA = Root Mean Squared Error of Approximation (scaled). SRMR = Standardized Root Mean Residual. Scaled chi-square, scaled df (degrees of freedom), and scaled p-value are reported. Best Fit indices are printed in bold typeface. Loadings higher than the loading of the self-reported physical item are printed in bold typeface.

results_secondary$table5
```
